---
title: "Activity: Graphical Exploration"
author: "eric weah"
date: "Due Date:2/9/2020 "
output: html_notebook
---



## Front Matter

Install supporting R packages with necessary functions and data sets.  You will need to add `library(DataComputing)` to the code chunk.  Note the line `rm(list = ls())` at the beginning of the code chunk, this will effectively reset your R environment which can help avoid bugs when an analysis gets more complicated.  


```{r} 
rm(list = ls())      # cleans up your R environment

# load packages
library(mosaic)
library(tidyverse)   # loads a group of useful packages including `ggplot2`


```



### Explore the `diamonds` data

*Task: Use R to produce one informative graphic of the `diamonds` data.  The graphic should represent AT LEAST 3 variables.  Write a few sentences to describe what we can learn from the graphic your have provided.  (Note: do NOT write your narrative inside the code chunk.)*

#The diamonds data has info on different carat dimonds. The data also shows how the dimaond was cut, the clarit, depth and pricing.
#The second ggplot shows the 3 varibales of cut, carat, and color. This can show that the bigger the carat the harder is it to get a better cut and diamond.

```{r}
# read `diamonds` data into R; it has been provided by the `ggplot2` package
data("diamonds", package = "ggplot2")

# add your code below for your one key data visualization

ggplot2::diamonds

ggplot() + geom_point(data = diamonds, aes(x = cut, y = carat, color = color))
```



### Explore the cereal data

*Task: Use R to produce one informative graphic of the `cereal.csv` data.  The graphic should represent AT LEAST 3 variables.  Write a few sentences to describe what we can learn from the graphic your have provided. (Note: do NOT write your narrative inside the code chunk.)*

#The dataset contains the nutritional value of cerals
#The graph produced shows a correlation between and rating. the lower the sugar the higher rating, the higher the sugar the lower the rating.

```{r}
# read CSV data set into R
CerealData <- read_csv(file = "cereal.csv")  



# add your code below for your one key data visualization
ggplot(CerealData, aes(sugars, rating)) +
 geom_point() 
  
```






### Extension: programming style

The helper functions are great, but they produce ugly code.  Clean up the `ggplot2` code that reproduces the required plots so that it aligns with the R Programming Style Guide Appendix in the *DataComputing* eBook <https://dtkaplan.github.io/DataComputingEbook/>.  


